### 2024-07-02 analysis/analysis.qmd
Edits of the preprocessing

## Sub-group analysis (based on model type)

@@

# Classify techniques according Hastie, Tibshirani, Friedman (2008)
#
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
# 3. Linear Methods for Regression
# 4. Linear Methods for Classification 
# 5. Basis Expansions and Regularization
# 6. Kernel Smoothing Methods
# 7. Model Assessment and Selection
# 8. Model Inference and Averaging 
# 9. Additive Models, Trees, and Related Methods
# 10. Boosting and Additive Trees
# 11. Neural Networks
# 12. Support Vector Machines and Flexible Discriminants
# 15. Random Forests
# 16. Ensemble Learning

# divide models into random forests, SVM and MLR
table(tmp$model_id)
tmp$model_class_id <- 'Unclassified'
tmp$model_class_id[str_detect(tmp$model_id,'lr|lm')] <- 'LR' # CAM?
tmp$model_class_id[str_detect(tmp$model_id,'PLS|MLR|gaussian|gmm|GMM|mlr|PLSR|sparse|variational bayesian')]<-'MLR/PLS'
tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression|forest|rfr')]<-'RF'
tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR|svr')]<-'SVM'
tmp$model_class_id[str_detect(tmp$model_id,'rnn')]<-'RNN'
tmp$model_class_id[str_detect(tmp$model_id,'bee|backprop|knn|mars|rbf|smoreg')]<-'NN other'
table(tmp$model_id,tmp$model_class_id)
tmp$model_class_id<-factor(tmp$model_class_id)

>>>>

## Organise modelling techniques used

@@

# Classify techniques according Hastie, Tibshirani, Friedman (2008)
#
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
# Replace with Cam's ## Linear Methods classes
# 3. Linear Methods for Regression
# 4. Linear Methods for Classification 
# 5. Basis Expansions and Regularization
# 6. Kernel Smoothing Methods
# 7. Model Assessment and Selection
# 8. Model Inference and Averaging 
# 9. Additive Models, Trees, and Related Methods
# 10. Boosting and Additive Trees
# 11. Neural Networks
# 12. Support Vector Machines and Flexible Discriminants
# 15. Random Forests
# 16. Ensemble Learning

# divide models into random forests, SVM and MLR
metaMER_results$model_id <- tolower(metaMER_results$model_id)
table(metaMER_results$model_id)
length(table(metaMER_results$model_id))
metaMER_results$model_class_id <- 'Unclassified'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Methods' # Class name from Elements of Stat.."
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal')]<-'Kernel Smoothing'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient')]<-'Random Forests'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'

table(metaMER_results$model_class_id)
round(table(metaMER_results$model_class_id)/nrow(metaMER_results),2)
table(metaMER_results$model_id[metaMER_results$model_class_id=='Unclassified'],metaMER_results$model_class_id[metaMER_results$model_class_id=='Unclassified'])

table(metaMER_results$model_class_id,metaMER_results$citekey)

table(metaMER_results$model_class_id,metaMER_results$model_category)

## simplify regression dimensions
metaMER_results$dimension[str_detect(metaMER_results$dimension,'xxxx')]<-'arousal'

table(metaMER_results$model_class_id,metaMER_results$dimension_category)
table(metaMER_results$model_class_id,metaMER_results$dimension)

View(metaMER_results)

mcan

table(tmp$model_id,tmp$model_class_id)
tmp$model_class_id<-factor(tmp$model_class_id)
